---
title: "Analysing fish invasion impact in french rivers "
date: "30/01/2017"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=TRUE }
knitr::opts_chunk$set(echo = FALSE)
library(vegan, verbose = F)
library(doBy)
library(ggplot2)
library(reshape2)
library(readxl)

Sys.setlocale("LC_ALL", 'en_US.UTF-8')


```



### Import, clean and check data

We are using public data from the ONEMA database.

```{r import, include=FALSE, message=FALSE, warning=TRUE}
source(file = 'scripts/import data.R')
```

### Exploratory analysis

Example of species richness in each river over time (here for rivers of Alsace with complete data in 2009-2013):
```{r}
SR = tapply(X = peches$`Nom usuel de l'espèce`,  INDEX = list( peches$Localisation , format(as.Date(peches$`Date de pêche`), "%Y") ), FUN =function(x)  length(x) )
meltdf <- melt(na.omit(SR))

ggplot(meltdf,aes(x=Var2,y=value,colour=Var1,group=Var1)) + geom_line(na.rm = T, show.legend = T) + labs(x = "year", y = "Species Richness", group ="Station")

```


Correlation of native vs. exotic richness at alpha scale.

Correlation of native vs. exotic richness at regional (watershed) scale.

### Comparing the impact of exotic fish on alpha and gamma fish diversity

Trends in local fish species richness along abundance gradient of exotic and other abundant fish.

Trends in regional richness along abundance gradient of exotic fish.


